---
format:
  dashboard:
    orientation: columns
aliases: 
  - home.html
project:
  output-dir: docs/
---
```{r}
#| message: FALSE
library(dplyr)
library(purrr)
library(stringr)
library(plotly)
library(Luciernaga)

Computer <- getwd()
MainFolder <- file.path(Computer, "data")
TheList <- c("3L", "4L", "5L", "CS")

# Updating Data
walk(.x=TheList, MainFolder=MainFolder, .f=Luciernaga:::DailyQCParse)
walk(.x=TheList, .f=Luciernaga:::QCBeadParse, MainFolder=MainFolder)
```

```{r}
MFI_3L <- Luciernaga:::CurrentData(x="3L", MainFolder=MainFolder, type = "MFI")
Gain_3L <- Luciernaga:::CurrentData(x="3L", MainFolder=MainFolder, type = "Gain")

MFI_4L <- Luciernaga:::CurrentData(x="4L", MainFolder=MainFolder, type = "MFI")
Gain_4L <- Luciernaga:::CurrentData(x="4L", MainFolder=MainFolder, type = "Gain")

MFI_5L <- Luciernaga:::CurrentData(x="5L", MainFolder=MainFolder, type = "MFI")
Gain_5L <- Luciernaga:::CurrentData(x="5L", MainFolder=MainFolder, type = "Gain")

MFI_CS <- Luciernaga:::CurrentData(x="CS", MainFolder=MainFolder, type = "MFI")
Gain_CS <- Luciernaga:::CurrentData(x="CS", MainFolder=MainFolder, type = "Gain")
```

```{r}
WindowOfInterest <- Sys.time() - months(12)

MFI_3L <- MFI_3L %>% filter(DateTime >= WindowOfInterest)
Gain_3L <- Gain_3L %>% filter(DateTime >= WindowOfInterest)

MFI_4L <- MFI_4L %>% filter(DateTime >= WindowOfInterest)
Gain_4L <- Gain_4L %>% filter(DateTime >= WindowOfInterest)

MFI_5L <- MFI_5L %>% filter(DateTime >= WindowOfInterest)
Gain_5L <- Gain_5L %>% filter(DateTime >= WindowOfInterest)

MFI_CS <- MFI_CS %>% filter(DateTime >= WindowOfInterest)
Gain_CS <- Gain_CS %>% filter(DateTime >= WindowOfInterest)
```

```{r}
Data <- read.csv("AuroraMaintenance.csv", check.names=FALSE)

Data <- Data %>% filter(!str_detect(reason, "lean"))

Repair3L <- Data %>% filter(instrument %in% "3L")
Repair4L <- Data %>% filter(instrument %in% "4L")
Repair5L <- Data %>% filter(instrument %in% "5L")
RepairCS <- Data %>% filter(instrument %in% "CS")
```


```{r}
The3L <- Luciernaga:::VisualQCSummary(x=Gain_3L)
The4L <- Luciernaga:::VisualQCSummary(x=Gain_4L)
The5L <- Luciernaga:::VisualQCSummary(x=Gain_5L)
TheCS <- Luciernaga:::VisualQCSummary(x=Gain_CS)
```

```{r}
Table3L <- Luciernaga:::SmallTable(data=The3L)
Table4L <- Luciernaga:::SmallTable(data=The4L)
Table5L <- Luciernaga:::SmallTable(data=The5L)
TableCS <- Luciernaga:::SmallTable(data=TheCS)
```

```{r}
#| include: false
#| echo: false
Data3L <- Luciernaga:::ShinyQCSummary(x=Gain_3L, Instrument="3L")
Data4L <- Luciernaga:::ShinyQCSummary(x=Gain_4L, Instrument="4L")
Data5L <- Luciernaga:::ShinyQCSummary(x=Gain_5L, Instrument="5L")
DataCS <- Luciernaga:::ShinyQCSummary(x=Gain_CS, Instrument="CS")

HistoricalData <- rbind(Data3L, Data4L, Data5L, DataCS)

Computer <- getwd()
MainFolder <- file.path(Computer, "data")
TheName <- "HistoricalData.csv"
HistoricalPath <- file.path(MainFolder, TheName)

write.csv(HistoricalData, HistoricalPath, row.names = FALSE)
```

```{r}
x <-  c("3L", "4L", "5L", "CS")
y <- list(Gain_3L, Gain_4L, Gain_5L, Gain_CS)

DataForPlot <- Luciernaga:::QCHistory(x=x, y=y)
Transposed <- t(DataForPlot)
colnames(Transposed) <- Transposed[1,]
Transposed <- Transposed[-1,]
DataForPlot <- data.frame(Transposed, check.names=FALSE)
DataForPlot <- DataForPlot %>% tibble::rownames_to_column(., var="Date")
DataForPlot$Date <- as.Date(DataForPlot$Date) 
Data <- DataForPlot %>% arrange(desc(Date))

GlobalSummary <- Luciernaga:::SmallTableGlobal(Data)
```

```{r}
TheDate <- Data %>% slice(1) %>% pull(Date)
```

```{r}
CurrentStatus <- function(data, x, type){
  Status <- data %>% select(all_of(x)) %>% na.omit() %>%
    slice(1) %>% pull()
  return(Status)
}

InstrumentText <- function(x) {
        dplyr::case_when(
          x == "Green" ~ "Pass",
          x == "Yellow" ~ "Caution",
          x == "Orange" ~ "Caution",
          x == "Red" ~ "Fail",
          TRUE ~ NA_character_ 
        )
      }

InstrumentColor <- function(x) {
        dplyr::case_when(
          x == "Green" ~ "success",
          x == "Yellow" ~ "caution",
          x == "Orange" ~ "warning",
          x == "Red" ~ "danger",
          TRUE ~ NA_character_ 
        )
}

TheStatus3L <- CurrentStatus(x="3L", data=Data) %>% InstrumentText(.)
TheColor3L <- CurrentStatus(x="3L", data=Data) %>% InstrumentColor(.)
TheStatus4L <- CurrentStatus(x="4L", data=Data) %>% InstrumentText(.)
TheColor4L <- CurrentStatus(x="4L", data=Data) %>% InstrumentColor(.)
TheStatus5L <- CurrentStatus(x="5L", data=Data) %>% InstrumentText(.)
TheColor5L <- CurrentStatus(x="5L", data=Data) %>% InstrumentColor(.)
TheStatusCS <- CurrentStatus(x="CS", data=Data) %>% InstrumentText(.)
TheColorCS <- CurrentStatus(x="CS", data=Data) %>% InstrumentColor(.)
```

## {.sidebar}
Dashboard data last updated on `r TheDate`

This dashboard contains the visualized QC data for the Cytek Auroras at the [UMGCC FCSS](https://www.medschool.umaryland.edu/cibr/core/umgccc_flow/)

For additional flow cytometry resources, visit our [website](https://sites.google.com/view/umgcccflow/home)

This dashboard was created with [Quarto](https://quarto.org/) and is maintained by [David Rach](https://github.com/DavidRach)

## First {width="30%"}

### Row {height="50%"}

#### Column

```{r}
#| content: valuebox
#| title: "3L"
#| icon: cup-hot

list(value = paste0("QC Status: ", TheStatus3L),
     color = TheColor3L)

```

#### Column

```{r}
#| content: valuebox
#| title: "4L"
#| icon: cup-hot

list(value = paste0("QC Status: ", TheStatus4L),
     color = TheColor4L)

```

### Row  {height="50%"}

#### Column

```{r}
#| content: valuebox
#| title: "5L"
#| icon: cup-hot

list(value = paste0("QC Status: ", TheStatus5L),
     color = TheColor5L)
```

#### Column {scrolling=FALSE}

```{r}
#| content: valuebox
#| title: "CS"
#| icon: cup-hot

list(value = paste0("QC Status: ", TheStatusCS),
     color = TheColorCS)
```

## Second {.tabset}
```{r}
#| title: 3L
Table3L
```

```{r}
#| title: 4L
Table4L
```

```{r}
#| title: 5L
Table5L
```

```{r}
#| title: CS
TableCS
```

::: {.card title="Today"}
:::

## Third {.tabset}{width="40%"}
```{r}
#| title: History
GlobalSummary
```