---
format:
  dashboard:
    orientation: columns
    scrolling: true
---

```{r}
#| message: FALSE
library(dplyr)
library(purrr)
library(stringr)
library(plotly)
library(Luciernaga)
library(flowCore)

Computer <- getwd()
MainFolder <- file.path(Computer, "data")
TheList <- c("LSRII")

CSTGates <- file.path(Computer, "Gates.csv")

# Updating Data (Work through later)
walk(.x=TheList, .f=Luciernaga:::HolisticQCParse, MainFolder=MainFolder, Template=CSTGates, subsets="Staining")
```

```{r}
LSRData <- Luciernaga:::CurrentData(x=TheList, MainFolder=MainFolder, type = "Both")
TheDate <- LSRData %>% slice(1) %>% pull(DATE)
```

```{r}
WindowOfInterest <- Sys.time() - months(12)

Both_LSR <- LSRData %>% filter(DateTime >= WindowOfInterest)
```

```{r}
Data <- read.csv("AuroraMaintenance.csv", check.names=FALSE)

Data <- Data %>% filter(!str_detect(reason, "lean"))

RepairLSR <- Data %>% filter(instrument %in% "LSRII")
```


```{r}
x <- Both_LSR
TheColumns <- x %>% select(where(~is.numeric(.)||is.integer(.))) %>% colnames()
TheColumns <- setdiff(TheColumns, "TIME")

# MFIs
TheIntermediate <- TheColumns[!str_detect(TheColumns, "Gain")]
TheColumnNames <- TheIntermediate[str_detect(TheIntermediate, "-A")]
  
VioletGains <- TheColumnNames[str_detect(TheColumnNames, "^V")]
BlueGains <- TheColumnNames[str_detect(TheColumnNames, "^B")]
YellowGreenGains <- TheColumnNames[str_detect(TheColumnNames, "^Y")]
RedGains <- TheColumnNames[str_detect(TheColumnNames, "^R")]

ScatterGains <- TheIntermediate[str_detect(TheIntermediate, "SC-")]
ScatterGains <- Luciernaga:::ScalePriority(ScatterGains)
LaserGains <- TheIntermediate[str_detect(TheIntermediate, "Laser")]
LaserGains <- Luciernaga:::ColorPriority(LaserGains)
ScalingGains <- TheIntermediate[str_detect(TheIntermediate, "Scaling")]
ScalingGains <- Luciernaga:::ColorPriority(ScalingGains)
OtherGains <- c(ScatterGains, LaserGains, ScalingGains)

VioletPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=VioletGains,
                      plotType = "individual", returntype = "plots",
                      Metadata="NULL", strict = TRUE, YAxisLabel = "MFI",
                      RepairVisits=RepairLSR)

BluePlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=BlueGains,
                      plotType = "individual", returntype = "plots",
                      Metadata=NULL, strict = TRUE, YAxisLabel = "MFI",
                      RepairVisits=RepairLSR)

YellowGreenPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=YellowGreenGains,
                     plotType = "individual", returntype = "plots",
                     Metadata=NULL, strict = TRUE, YAxisLabel = "MFI",
                     RepairVisits=RepairLSR)                      

RedPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=RedGains,
                     plotType = "individual", returntype = "plots",
                     Metadata=NULL, strict = TRUE, YAxisLabel = "MFI",
                     RepairVisits=RepairLSR)

ScatterPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=ScatterGains,
                     plotType = "individual", returntype = "plots",
                     Metadata=NULL, strict = TRUE, YAxisLabel = " ",
                     RepairVisits=RepairLSR)

LaserPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=LaserGains,
                     plotType = "individual", returntype = "plots",
                     Metadata=NULL, strict = TRUE, YAxisLabel = " ",
                     RepairVisits=RepairLSR)
```

```{r}
x <- Both_LSR
TheColumns <- x %>% select(where(~is.numeric(.)||is.integer(.))) %>% colnames()
TheColumns <- setdiff(TheColumns, "TIME")

# Gains
TheColumnNames <- TheColumns[str_detect(TheColumns, "Gain")]
TheColumnNames <- TheColumnNames[str_detect(TheColumnNames, "-A")]

VioletGains <- TheColumnNames[str_detect(TheColumnNames, "^V")]
BlueGains <- TheColumnNames[str_detect(TheColumnNames, "^B")]
YellowGreenGains <- TheColumnNames[str_detect(TheColumnNames, "^Y")]
RedGains <- TheColumnNames[str_detect(TheColumnNames, "^R")]

ScatterGains <- TheColumnNames[str_detect(TheColumnNames, "SC-")]
ScatterGains <- Luciernaga:::ScalePriority(ScatterGains)
LaserGains <- TheColumns[str_detect(TheColumns, "Laser")]
LaserGains <- Luciernaga:::ColorPriority(LaserGains)
ScalingGains <- TheColumns[str_detect(TheColumns, "Scaling")]
ScalingGains <- Luciernaga:::ColorPriority(ScalingGains)
OtherGains <- c(ScatterGains, LaserGains, ScalingGains)

VioletPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=VioletGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                      RepairVisits=RepairLSR)

BluePlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=BlueGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                      RepairVisits=RepairLSR)

YellowGreenPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=YellowGreenGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                     RepairVisits=RepairLSR)


RedPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=RedGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                     RepairVisits=RepairLSR)

ScatterPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=ScatterGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=RepairLSR)

LaserPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=LaserGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=RepairLSR)

ScalingPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=ScalingGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=RepairLSR)
```

```{r}
#| include: false
#| echo: false
PDFPlots <- c(VioletPlotsMFI, BluePlotsMFI, YellowGreenPlotsMFI, RedPlotsMFI, LaserPlotsMFI, ScatterPlotsMFI, VioletPlotsGain, BluePlotsGain, YellowGreenPlotsGain, RedPlotsGain, ScatterPlotsGain, LaserPlotsGain, ScalingPlotsGain)

Filename <- paste0("QCPlots_LSRII")

PDF <- Utility_Patchwork(x=PDFPlots, filename=Filename, returntype="pdf", outfolder=MainFolder, thecolumns=1)
```

## {.sidebar}
Dashboard data for the **BD LSR II** last updated on **`r TheDate`**

**First Column: MFI** Median Fluorescent Intensity (MFI) values for the QC beads. Measures stability over time. 
**Second Column: Gain** Gain (Voltage) values set for instrument after QC. Changes over time reflective of laser health. 

For additional information concerning individual parameter tabs, navigate to the [Help](https://umgccfcss.github.io/InstrumentQC/help) page.

**About**

This dashboard contains the visualized QC data for the Cytek and BD cytometers at the [UMGCC FCSS](https://www.medschool.umaryland.edu/cibr/core/umgccc_flow/)

For additional flow cytometry resources, visit our [website](https://sites.google.com/view/umgcccflow/home)

This dashboard was created with [Quarto](https://quarto.org/) and is maintained by [David Rach](https://github.com/DavidRach)


## MFI {.tabset}

```{r}
#| title: Violet
ggplotly(VioletPlotsMFI[[1]])
ggplotly(VioletPlotsMFI[[2]])
ggplotly(VioletPlotsMFI[[3]])
ggplotly(VioletPlotsMFI[[4]])
```

```{r}
#| title: Blue
ggplotly(BluePlotsMFI[[1]])
ggplotly(BluePlotsMFI[[2]])
```

```{r}
#| title: YellowGreen
ggplotly(YellowGreenPlotsMFI[[1]])
ggplotly(YellowGreenPlotsMFI[[2]])
ggplotly(YellowGreenPlotsMFI[[3]])
ggplotly(YellowGreenPlotsMFI[[4]])
```

```{r}
#| title: Red
ggplotly(RedPlotsMFI[[1]])
ggplotly(RedPlotsMFI[[2]])
ggplotly(RedPlotsMFI[[3]])
```

```{r}
#| title: Scatter
ggplotly(ScatterPlotsMFI[[1]])
ggplotly(ScatterPlotsMFI[[2]])
ggplotly(ScatterPlotsMFI[[3]])
ggplotly(ScatterPlotsMFI[[4]])
ggplotly(ScatterPlotsMFI[[5]])
ggplotly(ScatterPlotsMFI[[6]])
```

```{r}
#| title: LaserDelay
ggplotly(LaserPlotsGain[[1]])
ggplotly(LaserPlotsGain[[2]])
ggplotly(LaserPlotsGain[[3]])
ggplotly(LaserPlotsGain[[4]])
```

```{r}
#| title: LaserScaling
ggplotly(ScalingPlotsGain[[1]])
ggplotly(ScalingPlotsGain[[2]])
ggplotly(ScalingPlotsGain[[3]])
ggplotly(ScalingPlotsGain[[4]])
```

## Gain {.tabset}

```{r}
#| title: Violet
ggplotly(VioletPlotsGain[[1]])
ggplotly(VioletPlotsGain[[2]])
ggplotly(VioletPlotsGain[[3]])
ggplotly(VioletPlotsGain[[4]])
```

```{r}
#| title: Blue
ggplotly(BluePlotsGain[[1]])
ggplotly(BluePlotsGain[[2]])
```

```{r}
#| title: YellowGreen
ggplotly(YellowGreenPlotsGain[[1]])
ggplotly(YellowGreenPlotsGain[[2]])
ggplotly(YellowGreenPlotsGain[[3]])
ggplotly(YellowGreenPlotsGain[[4]])
```

```{r}
#| title: Red
ggplotly(RedPlotsGain[[1]])
ggplotly(RedPlotsGain[[2]])
ggplotly(RedPlotsGain[[3]])
```

```{r}
#| title: Scatter
ggplotly(ScatterPlotsGain[[1]])
ggplotly(LaserPlotsGain[[2]])
ggplotly(LaserPlotsGain[[2]])
ggplotly(ScatterPlotsGain[[2]])
ggplotly(LaserPlotsGain[[2]])
ggplotly(LaserPlotsGain[[2]])
```

```{r}
#| title: LaserDelay
ggplotly(LaserPlotsGain[[1]])
ggplotly(LaserPlotsGain[[2]])
ggplotly(LaserPlotsGain[[3]])
ggplotly(LaserPlotsGain[[4]])
```

```{r}
#| title: LaserScaling
ggplotly(ScalingPlotsGain[[1]])
ggplotly(ScalingPlotsGain[[2]])
ggplotly(ScalingPlotsGain[[3]])
ggplotly(ScalingPlotsGain[[4]])
```


